Ore Polynomials in Sage

### 2013-06-18 paper/main.tex
minor change in paper and one docstring.

Not every ring is suitable as base ring of an Ore algebra. Base rings must
themselves be polynomial rings (univariate or multivariate), or fraction 
fields of polynomial rings. Their base rings in turn may be either $\set Z$,
$\set Q$, a prime field $GF(p)$, or a number field $\set Q(\alpha)$, or
--- recursively --- some ring which itself would be suitable as base ring
of an Ore algebra.

>>>>

In theory, any integral domain can serve as base ring of an Ore algebra. Not so
in our implementation. Here, base rings must themselves be polynomial rings
(univariate or multivariate), or fraction fields of polynomial rings. Their base
rings in turn may be either $\set Z$, $\set Q$, a prime field $GF(p)$, or a
number field $\set Q(\alpha)$, or --- recursively --- some ring which itself
would be suitable as base ring of an Ore algebra.
